{\bf TODO: Intrusion Detection through Provenance}

### 2013-11-13 writeup/paper.tex
add design and implementation ideas and todos in other sections

\section{Design}
TODO

@@

\section{Evaluation}
TODO

@@

\section{Conclusion}
TODO

>>>>

\section{Design and Implementation}
TODO: ideas:
\begin{enumerate}
\item somayaji: sequence of system calls
\item semantic file attributes: determine types of files. use simple statistics on files.
\item histograms: use simple statistics and build histogram of file attributes on a process name/file
\item local clustering: use centrality metrics
\item fuzzy rules
\item hash k-tuples of provenance events and compare bit vectors
\item backwards and forwards causality graphs
\item access compatibility $\frac{1}{2}(C_d + C_e)$
\item intersect good DAG and bad DAG and look at intersection of DAG
\end{enumerate}

@@

\section{Evaluation}

\subsection{Evaluation Methodology}
TODO:
types of exploits we ran.
how we ran it.
how we collected the data.
the software we used.

\subsection{Results}
TODO:
true positives.
false positives.
graphs?

\subsection{Discussion}
TODO: 
why the numbers are the way they are.
what types of intrusions can we detect.
which provenance data is most useful

@@

\section{Conclusion and Future Work}
TODO
not realtime. can it be made to detect intrusions in realtime?
